---
title: "hw2"
author: "Qi Wang"
date: "2022/3/29"
output: 
  pdf_document:
        latex_engine: xelatex 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
rm(list = ls())
library(mvtnorm)
library(matrixsampling)
```
# Question 1: Hierarchical Model - School Treatment Effect
## Question 1a: Hierarchical Model - School Treatment Effect - Prior on Tau
```{r}
y <- c(28, 8, -3, 7, -1, 1, 18, 12)
sdy <- c(15, 10, 16, 11, 9, 11, 10, 18)
maxit <- 10000
theta <- matrix(NA, nrow = length(y), ncol = maxit)
mu <- tau <- rep(NA, maxit)
theta[,1] <- mean(y)
mu[1] <- mean(y)
tau[1] <- 10
i <- 1
for (i in 1:(maxit-1)) {
# Generate theta
  mean_vec <- (1/sdy^2 * y + 1/tau[i] * mu[i]) / (1/sdy^2 + 1/tau[i])
  cov_mat <- diag(1/(1/sdy^2 + 1/tau[i]), ncol = length(mean_vec))
  theta[,i+1] <- mvtnorm::rmvnorm(1, mean = mean_vec, sigma = cov_mat)

# Generate mu  
  mu[i+1] <- rnorm(1, mean = mean(theta[,i+1]), sd = sqrt(tau[i]/length(y)))
  
# Generate tau
  inv_tau <- rgamma(1, shape = (length(y)-1)/2, rate = sum( (theta[,i+1]-mu[i+1])^2 ) /2 )
  tau[i+1] <- 1/inv_tau
}
```

```{r}
thin <- seq(from = 2000, to = 10000, by = 8)
theta_final <- theta[,thin]
max_each <- apply(theta_final, 2, max)
best <- rep(NA, length(y))
for (j in 1:length(y)) {
  best[j] <- length(which(theta_final[j,] == max_each)) / length(thin)
}
best <- matrix(best, ncol = length(y))
colnames(best) <- AH <- c("A", "B", "C", "D", "E", "F", "G", "H")
knitr::kable(round(best,3), caption = "Probability of Best School - Prior on Tau", align = "c")
```

```{r}
pair_mat <- matrix(NA, length(y), length(y))

i<-j<-1

for (i in 1:length(y)) {
  for (j in 1:length(y)) {
    pair_mat[i,j] <- length(which(theta_final[i,] > theta_final[j,])) / length(thin)
  }
  
}
rownames(pair_mat) <- colnames(pair_mat) <- AH

knitr::kable(round(pair_mat,3), caption = "Pairwise Comparison - Prior on Tau (Row Index larger than Column Index)", align = "c" )

```

## Question 1b: Hierarchical Model - School Treatment Effect - Very Large Tau
```{r}
maxit <- 10000
theta <- matrix(NA, nrow = length(y), ncol = maxit)
mu <- rep(NA, maxit)
theta[,1] <- mean(y)
mu[1] <- mean(y)
tau <- 1e6
i <- 1
for (i in 1:(maxit-1)) {
#Generate theta
  mean_vec <- (1/sdy^2 * y + 1/tau * mu[i]) / (1/sdy^2 + 1/tau)
  cov_mat <- diag(1/(1/sdy^2 + 1/tau), ncol = length(mean_vec))
  theta[,i+1] <- mvtnorm::rmvnorm(1, mean = mean_vec, sigma = cov_mat)

#Generate mu  
  mu[i+1] <- rnorm(1, mean = mean(theta[,i+1]), sd = sqrt(tau/length(y)))
  
}
```

```{r}
thin <- seq(from = 2000, to = 10000, by = 8)
theta_final <- theta[,thin]
max_each <- apply(theta_final, 2, max)
best <- rep(NA, length(y))
for (j in 1:length(y)) {
  best[j] <- length(which(theta_final[j,] == max_each)) / length(thin)
}
best <- matrix(best, ncol = length(y))
colnames(best) <- AH <- c("A", "B", "C", "D", "E", "F", "G", "H")
knitr::kable(round(best,3), caption = "Probability of Best School - Tau Very Big", align = "c")
```

```{r}
pair_mat <- matrix(NA, length(y), length(y))

i<-j<-1

for (i in 1:length(y)) {
  for (j in 1:length(y)) {
    pair_mat[i,j] <- length(which(theta_final[i,] > theta_final[j,])) / length(thin)
  }
  
}
rownames(pair_mat) <- colnames(pair_mat) <- AH

knitr::kable(round(pair_mat,3), caption = "Pairwise Comparison - Tau Very Big (Row Index larger than Column Index)", align = "c" )

```

## Question 1b: Hierarchical Model - School Treatment Effect - Very Small Tau
```{r}
maxit <- 10000
theta <- matrix(NA, nrow = length(y), ncol = maxit)
mu <- rep(NA, maxit)
theta[,1] <- mean(y)
mu[1] <- mean(y)
tau <- 1e-20
i <- 1
for (i in 1:(maxit-1)) {
#Generate theta
  mean_vec <- (1/sdy^2 * y + 1/tau * mu[i]) / (1/sdy^2 + 1/tau)
  cov_mat <- diag(1/(1/sdy^2 + 1/tau), ncol = length(mean_vec))
  theta[,i+1] <- mvtnorm::rmvnorm(1, mean = mean_vec, sigma = cov_mat)

#Generate mu  
  mu[i+1] <- rnorm(1, mean = mean(theta[,i+1]), sd = sqrt(tau/length(y)))
  
}
```

```{r}
thin <- seq(from = 2000, to = 10000, by = 8)
theta_final <- theta[,thin]
max_each <- apply(theta_final, 2, max)
best <- rep(NA, length(y))
for (j in 1:length(y)) {
  best[j] <- length(which(theta_final[j,] == max_each)) / length(thin)
}
best <- matrix(best, ncol = length(y))
colnames(best) <- AH <- c("A", "B", "C", "D", "E", "F", "G", "H")
knitr::kable(round(best,3), caption = "Probability of Best School - Tau Very Small", align = "c")
```



```{r}
pair_mat <- matrix(NA, length(y), length(y))

i<-j<-1

for (i in 1:length(y)) {
  for (j in 1:length(y)) {
    pair_mat[i,j] <- length(which(theta_final[i,] > theta_final[j,])) / length(thin)
  }
  
}
rownames(pair_mat) <- colnames(pair_mat) <- AH

knitr::kable(round(pair_mat,3), caption = "Pairwise Comparison - Tau Very Small (Row Index larger than Column Index)", align = "c" )

```

# Question 2: Mixture Model

```{r}
x <- seq(from = -3, to = 3, by = 0.01)
ybar <- -0.25

pri <- 0.8*dnorm(x, mean = 1, sd = 0.5) + 0.2*dnorm(x, mean = -1, sd = 0.5)
posw <- c(0.8*exp(41/4*ybar^2), 0.2*exp(41/4 *(39/41)^2*ybar^2))
posw_n <- posw/sum(posw)
pos <- posw_n[1] * dnorm(x, mean = ybar, sd = sqrt(4/41)) + posw_n[2] * dnorm(x, mean = 39/41*ybar, sd = sqrt(4/41))
plot(x = x, y = pri, type = 'l', col = 'red', lwd = 2, ylim = c(0,1.5), main = "Prior and Posterior Density", ylab = "Probability", xlab = "")
lines(x = x, y = pos, type = 'l', col = 'blue', lwd = 2)
legend("topleft", c("Prior", "Posterior"), col = c("red","blue"), lty = c(1,1), lwd = c(2,2))
```  

# Question 3: Hierachical Beta Distribution  


## Question 3.b: Hierachical Beta Distribution - Marginal Posterior for Hyperparameter
```{r}
yj <- c(16, 9, 10, 13, 19, 20, 18, 17, 35, 55)
y2 <- c(58, 90, 48, 57, 103, 57, 86, 112, 273, 64)
nj <- yj + y2
N <- length(yj)


alpha <- seq(from = 0.01, to = 6, by = 0.01)
beta <- seq(from = 0.01, to = 15, by = 0.01)

pos <- matrix(NA, nrow = length(alpha), ncol = length(beta))
pos_fun <- function(alpha, beta){
  out <- (alpha + beta)^(-5/2) * ( beta(a = alpha, b = beta) )^(-N) *
    prod( beta(a = alpha + yj, b = beta + nj - yj)   )  
  return(out)
}

```

```{r}
i <- j <- 1
for (i in 1:length(alpha)) {
  for (j in 1:length(beta)) {
    pos[i,j] <- pos_fun(alpha = alpha[i], beta = beta[j])
  }
  
}

```

```{r}
contour(x = alpha, y = beta, z = pos/sum(pos), nlevels = 8, xlab = "Alpha", ylab = "Beta", main = "Marginal Posterior Density of Hyperparameters")
```

```{r}
samplesize <- 1000
sample_alpha_index <- rep(NA, samplesize)
sample_beta_index <- rep(NA, samplesize)

i <-1
for (i in 1:samplesize) {
  sample_alpha_index[i] <- sample(1:length(alpha), size = 1, prob = rowSums(pos))
  sample_beta_index[i] <- sample(1:length(beta), size = 1, prob = pos[sample_alpha_index[i],])
}
```


```{r}

sample_alpha <- alpha[sample_alpha_index]
sample_beta <- beta[sample_beta_index]
sample_theta <- matrix(NA, ncol = samplesize, nrow = N)
den <- MASS::kde2d(x = sample_alpha, y = sample_beta)
contour(x = den$x, y = den$y, z = den$z, xlab = "Alpha", ylab = "Beta", main = "Sampling Distribution of Hyperparameters")
i <- j <- 1
for (i in 1:N) {
  for (j in 1:samplesize) {
    sample_theta[i,j] <- rbeta(1, shape1 = sample_alpha[j]+yj[i], shape2 = nj[i] + sample_beta[j] - yj[i])
  }
}
```
```{r}
i <- 1
par(mfrow = c(3,4))
for (i in 1:N) {
  plot(density(sample_theta[i,]), type = "l", main = paste("Posterior of", "Theta", i), lwd = 2, xlab = paste("theta", i), ylab = "Probability")
  abline(v = (yj/nj)[i], lwd = 2, col = "red")
}
```
```{r}
set.seed(0)
i <- 1
theta_average <- rep(NA, samplesize)
for (i in 1:samplesize) {
  theta_average[i] <- rbeta(1, shape1 = sample_alpha, shape2 = sample_beta)
}
plot(density(theta_average), type = 'l', xlab = "Overall Theta", ylab = "Probability", main = "Overall Theta Density Plot", col = "red", lwd = 2)
CI <- round(c(quantile(theta_average, 0.025),quantile(theta_average, 0.975)), 3)
print(CI)
```


```{r}
i <-1
new_alpha_index <- new_beta_index <- rep(NA, samplesize)
new_theta <- rep(NA, samplesize)
for (i in 1:samplesize) {
  new_alpha_index[i] <- sample(1:length(alpha), size = 1, prob = rowSums(pos))
  new_beta_index[i] <- sample(1:length(beta), size = 1, prob = pos[new_alpha_index[i],])
}

new_alpha <- alpha[new_alpha_index]
new_beta <- beta[new_beta_index]
new_theta <- matrix(NA, ncol = samplesize, nrow = N)

i <- j <- 1
for (i in 1:samplesize) {
  
    new_theta[i] <- rbeta(1, shape1 = new_alpha[i], shape2 = new_beta[i])
  
}
```

```{r}
new_y <- rep(NA, samplesize)
i <- 1
for (i in 1: samplesize){
  new_y[i] <- rbinom(1, size = 100, prob = new_theta[i])
}
CI <- round(c(quantile(new_y, 0.025),quantile(new_y, 0.975)), 3)
plot(density(new_y), type = 'l', xlab = "New y", ylab = "Probability", main = "Predictive Density", col = "red", lwd = 2)
print(CI)
```
# Question 5: NIW Distribution

## K = 2

```{r}
#Initialize
X <- read.csv(here::here("SimMovieRating.csv"))
X <- as.matrix(X)
K <- 2
k0 <- 2
iter <- 10000
n <- 100
p <- 30

#Initialize UV
U <- array(NA, dim = c(K,n,iter))
V <- array(NA, dim = c(K,p,iter))
U[,,1] <- 1
V[,,1] <- 1
#Initialize mean of u and v
mu_u <- matrix(NA, nrow = K, ncol = iter )
mu_v <- matrix(NA, nrow = K, ncol = iter )
mu_u[,1] <- 1
mu_v[,1] <- 1
#Initialize covariance matrix
sig_u <- array(NA, dim = c(K,K,iter))
sig_v <- array(NA, dim = c(K,K,iter))
sig_u[,,1] <- diag(1, nrow = K)
sig_v[,,1] <- diag(1, nrow = K)
```


```{r}
#Gibbs Sampler
i <- 1
for (i in 1:(iter-1)) {
  #Sample Ui
  for (m in 1:n) {
    mean_vec <- solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i])) %*%(V[,,i] %*% X[m,] + solve(sig_u[,,i]) %*% as.matrix(mu_u[,i]))
    cov_mat <-  solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i]))
    U[,m,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample Vi
  for (l in 1:p) {
    mean_vec <- solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i])) %*%(U[,,i+1] %*% X[,l] + solve(sig_v[,,i]) %*% as.matrix(mu_v[,i]))
    cov_mat <-  solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i]))
    V[,l,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample mean of u
  mean_vec <- rowSums(U[,,i+1]) / (n + k0)
  cov_mat <- sig_u[,,i]/(n + k0)
  mu_u[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample mean of v  
  mean_vec <- rowSums(V[,,i+1]) / (p + k0)
  cov_mat <- sig_v[,,i]/(p + k0)
  mu_v[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample Sigma of u
  nu <- n + p + 1
  lambda <- k0  * as.matrix(mu_u[,i+1]) %*% t(as.matrix(mu_u[,i+1])) + diag(1, nrow = K, ncol = K ) + (U[,,i+1] - mu_u[,i+1]) %*% t(U[,,i+1] - mu_u[,i+1])
  sig_u[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
  #Sample Sigma of v
  nu <- p + p + 2
  lambda <- k0  * as.matrix(mu_v[,i+1]) %*% t(as.matrix(mu_v[,i+1])) + diag(1, nrow = K, ncol = K ) + (V[,,i+1] - mu_v[,i+1]) %*% t(V[,,i+1] - mu_v[,i+1])
  sig_v[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
}

```
```{r}
Vm_2 <- round(t(apply(V, c(1,2), mean)),4)
movie_id <- paste("Movie",1:p)
K_names <- 1:K
rownames(Vm_2) <- movie_id
colnames(Vm_2) <- K_names
knitr::kable(Vm_2, caption = "V Matrix", assign = 'c')
```


## K = 4
```{r}
#Initialize
X <- read.csv(here::here("SimMovieRating.csv"))
X <- as.matrix(X)
K <- 4
k0 <- 2
iter <- 10000
n <- 100
p <- 30

#Initialize UV
U <- array(NA, dim = c(K,n,iter))
V <- array(NA, dim = c(K,p,iter))
U[,,1] <- 1
V[,,1] <- 1
#Initialize mean of u and v
mu_u <- matrix(NA, nrow = K, ncol = iter )
mu_v <- matrix(NA, nrow = K, ncol = iter )
mu_u[,1] <- 1
mu_v[,1] <- 1
#Initialize covariance matrix
sig_u <- array(NA, dim = c(K,K,iter))
sig_v <- array(NA, dim = c(K,K,iter))
sig_u[,,1] <- diag(1, nrow = K)
sig_v[,,1] <- diag(1, nrow = K)
```


```{r}
#Gibbs Sampler
i <- 1
for (i in 1:(iter-1)) {
  #Sample Ui
  for (m in 1:n) {
    mean_vec <- solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i])) %*%(V[,,i] %*% X[m,] + solve(sig_u[,,i]) %*% as.matrix(mu_u[,i]))
    cov_mat <-  solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i]))
    U[,m,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample Vi
  for (l in 1:p) {
    mean_vec <- solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i])) %*%(U[,,i+1] %*% X[,l] + solve(sig_v[,,i]) %*% as.matrix(mu_v[,i]))
    cov_mat <-  solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i]))
    V[,l,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample mean of u
  mean_vec <- rowSums(U[,,i+1]) / (n + k0)
  cov_mat <- sig_u[,,i]/(n + k0)
  mu_u[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample mean of v  
  mean_vec <- rowSums(V[,,i+1]) / (n + k0)
  cov_mat <- sig_v[,,i]/(p + k0)
  mu_v[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample Sigma of u
  nu <- n + p + 1
  lambda <- k0  * as.matrix(mu_u[,i+1]) %*% t(as.matrix(mu_u[,i+1])) + diag(1, nrow = K, ncol = K ) + (U[,,i+1] - mu_u[,i+1]) %*% t(U[,,i+1] - mu_u[,i+1])
  sig_u[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
  #Sample Sigma of v
  nu <- p + p + 2
  lambda <- k0  * as.matrix(mu_v[,i+1]) %*% t(as.matrix(mu_v[,i+1])) + diag(1, nrow = K, ncol = K ) + (V[,,i+1] - mu_v[,i+1]) %*% t(V[,,i+1] - mu_v[,i+1])
  sig_v[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
}

```
```{r}
Vm_4 <- round(t(apply(V, c(1,2), mean)),4)
movie_id <- paste("Movie",1:p)
K_names <- 1:K
rownames(Vm_4) <- movie_id
colnames(Vm_4) <- K_names
knitr::kable(Vm_4, caption = "V Matrix", assign = 'c')
```

## K = 6
```{r}
#Initialize
X <- read.csv(here::here("SimMovieRating.csv"))
X <- as.matrix(X)
K <- 6
k0 <- 2
iter <- 10000
n <- 100
p <- 30

#Initialize UV
U <- array(NA, dim = c(K,n,iter))
V <- array(NA, dim = c(K,p,iter))
U[,,1] <- 1
V[,,1] <- 1
#Initialize mean of u and v
mu_u <- matrix(NA, nrow = K, ncol = iter )
mu_v <- matrix(NA, nrow = K, ncol = iter )
mu_u[,1] <- 1
mu_v[,1] <- 1
#Initialize covariance matrix
sig_u <- array(NA, dim = c(K,K,iter))
sig_v <- array(NA, dim = c(K,K,iter))
sig_u[,,1] <- diag(1, nrow = K)
sig_v[,,1] <- diag(1, nrow = K)
```


```{r}
#Gibbs Sampler
i <- 1
for (i in 1:(iter-1)) {
  #Sample Ui
  for (m in 1:n) {
    mean_vec <- solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i])) %*%(V[,,i] %*% X[m,] + solve(sig_u[,,i]) %*% as.matrix(mu_u[,i]))
    cov_mat <-  solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i]))
    U[,m,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample Vi
  for (l in 1:p) {
    mean_vec <- solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i])) %*%(U[,,i+1] %*% X[,l] + solve(sig_v[,,i]) %*% as.matrix(mu_v[,i]))
    cov_mat <-  solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i]))
    V[,l,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample mean of u
  mean_vec <- rowSums(U[,,i+1]) / (n + k0)
  cov_mat <- sig_u[,,i]/(n + k0)
  mu_u[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample mean of v  
  mean_vec <- rowSums(V[,,i+1]) / (n + k0)
  cov_mat <- sig_v[,,i]/(p + k0)
  mu_v[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample Sigma of u
  nu <- n + p + 1
  lambda <- k0  * as.matrix(mu_u[,i+1]) %*% t(as.matrix(mu_u[,i+1])) + diag(1, nrow = K, ncol = K ) + (U[,,i+1] - mu_u[,i+1]) %*% t(U[,,i+1] - mu_u[,i+1])
  sig_u[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
  #Sample Sigma of v
  nu <- p + p + 2
  lambda <- k0  * as.matrix(mu_v[,i+1]) %*% t(as.matrix(mu_v[,i+1])) + diag(1, nrow = K, ncol = K ) + (V[,,i+1] - mu_v[,i+1]) %*% t(V[,,i+1] - mu_v[,i+1])
  sig_v[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
}

```
```{r}
Vm_6 <- round(t(apply(V, c(1,2), mean)),4)
movie_id <- paste("Movie",1:p)
K_names <- 1:K
rownames(Vm_6) <- movie_id
colnames(Vm_6) <- K_names
knitr::kable(Vm_6, caption = "V Matrix", assign = 'c')
```


## K = 8
```{r}
#Initialize
X <- read.csv(here::here("SimMovieRating.csv"))
X <- as.matrix(X)
K <- 8
k0 <- 2
iter <- 10000
n <- 100
p <- 30

#Initialize UV
U <- array(NA, dim = c(K,n,iter))
V <- array(NA, dim = c(K,p,iter))
U[,,1] <- 1
V[,,1] <- 1
#Initialize mean of u and v
mu_u <- matrix(NA, nrow = K, ncol = iter )
mu_v <- matrix(NA, nrow = K, ncol = iter )
mu_u[,1] <- 1
mu_v[,1] <- 1
#Initialize covariance matrix
sig_u <- array(NA, dim = c(K,K,iter))
sig_v <- array(NA, dim = c(K,K,iter))
sig_u[,,1] <- diag(1, nrow = K)
sig_v[,,1] <- diag(1, nrow = K)
```


```{r}
#Gibbs Sampler
i <- 1
for (i in 1:(iter-1)) {
  #Sample Ui
  for (m in 1:n) {
    mean_vec <- solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i])) %*%(V[,,i] %*% X[m,] + solve(sig_u[,,i]) %*% as.matrix(mu_u[,i]))
    cov_mat <-  solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i]))
    U[,m,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample Vi
  for (l in 1:p) {
    mean_vec <- solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i])) %*%(U[,,i+1] %*% X[,l] + solve(sig_v[,,i]) %*% as.matrix(mu_v[,i]))
    cov_mat <-  solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i]))
    V[,l,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample mean of u
  mean_vec <- rowSums(U[,,i+1]) / (n + k0)
  cov_mat <- sig_u[,,i]/(n + k0)
  mu_u[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample mean of v  
  mean_vec <- rowSums(V[,,i+1]) / (n + k0)
  cov_mat <- sig_v[,,i]/(p + k0)
  mu_v[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample Sigma of u
  nu <- n + p + 1
  lambda <- k0  * as.matrix(mu_u[,i+1]) %*% t(as.matrix(mu_u[,i+1])) + diag(1, nrow = K, ncol = K ) + (U[,,i+1] - mu_u[,i+1]) %*% t(U[,,i+1] - mu_u[,i+1])
  sig_u[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
  #Sample Sigma of v
  nu <- p + p + 2
  lambda <- k0  * as.matrix(mu_v[,i+1]) %*% t(as.matrix(mu_v[,i+1])) + diag(1, nrow = K, ncol = K ) + (V[,,i+1] - mu_v[,i+1]) %*% t(V[,,i+1] - mu_v[,i+1])
  sig_v[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
}

```
```{r}
Vm_8 <- round(t(apply(V, c(1,2), mean)),4)
movie_id <- paste("Movie",1:p)
K_names <- 1:K
rownames(Vm_8) <- movie_id
colnames(Vm_8) <- K_names
knitr::kable(Vm_8, caption = "V Matrix", assign = 'c')
```


## K = 10
```{r}
#Initialize
X <- read.csv(here::here("SimMovieRating.csv"))
X <- as.matrix(X)
K <- 10
k0 <- 2
iter <- 10000
n <- 100
p <- 30

#Initialize UV
U <- array(NA, dim = c(K,n,iter))
V <- array(NA, dim = c(K,p,iter))
U[,,1] <- 1
V[,,1] <- 1
#Initialize mean of u and v
mu_u <- matrix(NA, nrow = K, ncol = iter )
mu_v <- matrix(NA, nrow = K, ncol = iter )
mu_u[,1] <- 1
mu_v[,1] <- 1
#Initialize covariance matrix
sig_u <- array(NA, dim = c(K,K,iter))
sig_v <- array(NA, dim = c(K,K,iter))
sig_u[,,1] <- diag(1, nrow = K)
sig_v[,,1] <- diag(1, nrow = K)
```


```{r}
#Gibbs Sampler
i <- 1
for (i in 1:(iter-1)) {
#Sample Ui
  for (m in 1:n) {
    mean_vec <- solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i])) %*%(V[,,i] %*% X[m,] + solve(sig_u[,,i]) %*% as.matrix(mu_u[,i]))
    cov_mat <-  solve(V[,,i]%*%t(V[,,i]) + solve(sig_u[,,i]))
    U[,m,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample Vi
  for (l in 1:p) {
    mean_vec <- solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i])) %*%(U[,,i+1] %*% X[,l] + solve(sig_v[,,i]) %*% as.matrix(mu_v[,i]))
    cov_mat <-  solve(U[,,i+1]%*%t(U[,,i+1]) + solve(sig_v[,,i]))
    V[,l,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  }
  #Sample mean of u
  mean_vec <- rowSums(U[,,i+1]) / (n + k0)
  cov_mat <- sig_u[,,i]/(n + k0)
  mu_u[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample mean of v  
  mean_vec <- rowSums(V[,,i+1]) / (n + k0)
  cov_mat <- sig_v[,,i]/(p + k0)
  mu_v[,i+1] <- rmvnorm(1, mean = mean_vec, sigma = cov_mat)
  #Sample Sigma of u
  nu <- n + p + 1
  lambda <- k0  * as.matrix(mu_u[,i+1]) %*% t(as.matrix(mu_u[,i+1])) + diag(1, nrow = K, ncol = K ) + (U[,,i+1] - mu_u[,i+1]) %*% t(U[,,i+1] - mu_u[,i+1])
  sig_u[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
  #Sample Sigma of v
  nu <- p + p + 2
  lambda <- k0  * as.matrix(mu_v[,i+1]) %*% t(as.matrix(mu_v[,i+1])) + diag(1, nrow = K, ncol = K ) + (V[,,i+1] - mu_v[,i+1]) %*% t(V[,,i+1] - mu_v[,i+1])
  sig_v[,,i+1] <- rinvwishart(1, nu = nu, Omega = lambda)
}

```
```{r}
Vm_10 <- round(t(apply(V, c(1,2), mean)),4)
movie_id <- paste("Movie",1:p)
K_names <- 1:K
rownames(Vm_10) <- movie_id
colnames(Vm_10) <- K_names
knitr::kable(Vm_10, caption = "V Matrix", assign = 'c')
```

# Question 6: Poisson-Gamma Distribution
```{r}
ti <- c(94.3, 15.7, 62.9, 126, 5.24, 31.4, 1.05, 1.05, 2.1, 10.5)
yi <- c(5, 1, 5, 14, 3, 19, 1, 1, 4, 22)
iter <- 10000
a <- 0.1
b <- 10
n <- length(ti)
rw_step <- 0.5
alpha_pos <- rep(NA, iter)
beta_pos <- rep(NA, iter)
alpha_pos[1] <- 10
beta_pos[1] <- 10
theta_pos <- matrix(NA, nrow = length(ti), ncol = iter)
theta_pos[,1] <- 1

p_log <- function(t, beta, theta){
  out <- prod(theta)^(exp(t)-1) * exp(t - exp(t)) * (beta^exp(t) / gamma(exp(t)))^n
    return(out)
}
  rg <- Vectorize(rgamma)
```

```{r}
for (i in 1:(iter-1)) {
  # Generate beta
  beta_pos[i + 1] <- rgamma(1, shape = a + alpha_pos[i]*n, rate = b + sum(theta_pos[,i]))
  #Generate alpha
  alpha_new_log <- rnorm(1, mean = log(alpha_pos[i]), sd = rw_step)
  p <- p_log(t = alpha_new_log, beta = beta_pos[i+1], theta = theta_pos[,i])/p_log(t = log(alpha_pos[i]), beta = beta_pos[i+1], theta = theta_pos[,i])
  index <- runif(1)
  if(index <= p){
   alpha_pos[i+1] <- exp(alpha_new_log) 
  }else{alpha_pos[i+1] <- alpha_pos[i]}
  #Generate theta
  param_alpha <- alpha_pos[i+1] + yi
  param_beta <- beta_pos[i+1] +ti
  theta_pos[,i+1] <- unlist(rg(n = rep(1, length(yi)), shape = param_alpha, rate = param_beta  ) )
  
}


```

```{r}
thin <- seq(from = 2000, to = 10000, by = 8)
par(mfrow = c(1,2))
hist(alpha_pos[thin], main = "Marginal Distribution of Alpha", xlab = "Alpha", col = 'lightblue', probability = TRUE)
hist(beta_pos[thin], main = "Marginal Distribution of Beta", xlab = "Beta", col = 'lightpink' , probability = TRUE)

```
```{r}
plot(x =alpha_pos[thin], y = beta_pos[thin], xlab = "Alpha", ylab = "Beta", pch = 19 )
```

## MH to sample Marginal Distribution

```{r}
log_alpha <- rep(NA, iter)
log_beta <- rep(NA, iter)
log_alpha[1] <- 1
log_beta[1] <- 1
sig <- diag(0.1, 2,2)
pos_den <- function(ta, tb){
  
  out <- exp(-exp(ta)-b*exp(tb)) * exp(tb)^(n*exp(ta)+a-1)/ prod(  ( exp(tb) + ti)^(exp(ta)+yi)  ) * prod(gamma(exp(ta)+yi)) / gamma(exp(ta))^n * exp(ta + tb)
  return(out)
  
}

```

```{r}
i <- 1
for (i in 1:(iter-1)) {
  newpair <- rmvnorm(1, mean = c(log_alpha[i], log_beta[i]), sigma = sig)
  p <- pos_den(ta = newpair[1], tb = newpair[2]) / pos_den(ta = log_alpha[i], tb = log_beta[i])
  index <- runif(1)
  if(index <= p){
    log_alpha[i+1] <- newpair[1]
    log_beta[i+1] <- newpair[2]
  }else{
    log_alpha[i+1] <- log_alpha[i]
    log_beta[i+1] <- log_beta[i]
  }
}
```
```{r}
alpha_margin <- exp(log_alpha[thin])
beta_margin <- exp(log_beta[thin])


par(mfrow = c(1,2))
hist(alpha_margin, main = "Marginal Distribution of Alpha", xlab = "Alpha", col = 'lightblue', probability = TRUE)
hist(beta_margin, main = "Marginal Distribution of Beta", xlab = "Beta", col = 'lightpink' , probability = TRUE)


```

```{r}
plot(x =alpha_margin, y = beta_margin, xlab = "Alpha", ylab = "Beta", pch = 19 )
```



